\section{Background}

\subsection{Introduction to the iVotronic DRE}
A brief description of the iVotronic’s functionality and main system components follows:

\begin{itemize} 
\item Voting terminal. The voting terminal is a stand-alone touchscreen voting unit.  The terminal is equipped with an internal battery which keeps the unit operational in the event of a power failure, and a removable compact flash card, which is used to store audit data and ballot images (cast vote records). Typically, each polling location is assigned several iVotronic machines. Also, to comply with the federal American with Disabilities Act, at least one audio terminal is placed in each precinct to assist visually impaired voters.

\item Personalized Electronic Ballot (PEB). The PEB is a proprietary cartridge designed by ES\&S to operate the iVotronic terminal.  When the PEB is placed in the machine, the terminal and the PEB can communicate through the infrared port.  Typically, counties deploy two types of PEB to the precinct: a) a green band master PEB and b) a red band activator PEB. Both type of PEBs have the same functionality, however, poll workers are trained to keep them separate and use them for different purposes.
    \begin{itemize}
    \item Master PEB:  Poll workers use the master PEB to open polls on election day. When the PEB is placed in the terminal, the touchscreen displays the precinct's name programmed in the PEB so that poll workers can verify the polling location information and date/time registered in the terminal's internal clock. If the information displayed is correct, the poll workers open the terminal for voting. The same master PEB should be used to open all terminals in the polling location. In the same fashion, the master PEB should be used to close all terminals in the polling location at the end of the voting day. When the terminal is closed, it uploads its vote totals onto the PEB inserted into it. If the master PEB is used to close all terminals , this PEB accumulates the precinct totals so that they can later be uploaded and included in the official tally.
    \item Activator PEBs.  Activator PEBs are used by  poll workers to activate ballots for voters. Election officials provide each precinct with multiple Activator PEBs. Internally, all PEBs at the precinct are identical. The only difference between them is the color of the rubber band on their exterior. Thus, a Master PEB can be used to activate a voter's ballot and an Activator PEB can be used to open and close terminals. Though as a matter of procedure and training, they should not be used this way. If an Activator PEB is used to close terminals, the precinct vote totals may be partially uploaded to the aggregated totals on election night. Poll workers are training so that they put the Master PEB, CF cards and precinct's total tapes in a designated bag that is transported to Election Central after polls close.  Activator PEBs used to close terminals may be left behind and their vote data not added to the certified count.
    \end{itemize}
\item Removable Compact Flash card (CF). The CF cards are programmed at Election Central and installed in the back of the voting terminal prior to deployment at the polling location. The CF cards contain graphic (bitmap) files read by the voting terminal during the voting process. The CF cards are also used as an external memory device: audit log entries and ballot images are written to the CF card when the terminal is closed for voting. Once the polls close, the CF cards are removed from the back of the terminal and delivered to election headquarters on election night. 

\item External printer module: This module is connected to a serial port on the back of the voting terminal. The thermal printer produces the precinct zero tape and results tape. Poll workers are instructed to print the zero tape once all iVotronics of the precinct are opened for voting. In the same fashion, they are training to print the results tape when all voting terminals are closed for voting on election night.
\end{itemize}

\subsection{iVotronic Audit}
The ES\&S voting solution produces many log files including the Election Reporting Manager (ERM) \textquotedblleft System Log\textquotedblright \hspace{1 mm} file, the ERM \textquotedblleft Result Correction Log,\textquotedblright \hspace{1 mm} the ERM \textquotedblleft Real Time Log,\textquotedblright \hspace{1 mm} the iVotronic \textquotedblleft Ballot Image\textquotedblright \hspace{1 mm} log and the iVotronic \textquotedblleft Event Log.\textquotedblright \hspace{2 mm} We focused on three: the event log (EL152.lst), ballot image file (EL155.lst), and the system log (EL68a.lst).  The header of the log files identify the county's name, the type and date of the election, the date the report was generated, and the election ID. The election ID is a parameter generated by the ES\&S election programming software to uniquely identify each election. 
 
The event log (EL152.lst) contains audit log entries from each iVotronic terminal used on the election.  The log  records, in  chronological order, all events that occurred on that machine in this election. It typically begins with \textquotedblleft clear and test\textquotedblright \hspace{1 mm} of the terminal to delete previous election data from the terminal's memory, performed at election headquarters before the election. It also records, in chronological order, all election day events, including polls open and polls closing and the number of ballots cast.  Each event log entry includes the iVotronic's terminal serial number, the PEB's serial number, the date and time, the event occurred and a description of the event. An excerpt of  an event log is given in  Appendix~\ref{app:el}. 
 
The ballot image file (EL155.lst) contains all ballot images saved by the iVotronic terminals during the voting process. In ES\&S terminology is a list of all choices made by a single voter (i.e., a cast vote record); it is not a scanned or photographic image. The ballot images are segregated by precinct and terminal where the votes were cast. The ballots are saved in a random order to protect the privacy of the voter.  An excerpt of a ballot image file is given in  Appendix~\ref{app:bi}
 
The system log listing file (EL68a.lst) tracks activity in the election reporting database since its creation at the election headquarters. Its chronological entries reflect the commands executed by the operators during  pre-election testing, election night reporting, and post-election canvassing. It also contains the totals accumulated in the various precincts during election night reporting, as well as any warnings or errors reported by the reporting software system during the tabulation process. The system log also tracks the uploading of PEBs and CF cards to the central election reporting database. Manual adjustment of precinct totals are also documented in the system log file. An excerpt of a system log file is given in Appendix~\ref{app:sl}.
