\section{Future Voting System Suggestions}
Voting systems audit logs need to be readable, orderly and their message should
be  comprehensible to the public. Ambiguous or obscure messages will make audit
logs unusable to election officials and advocacy groups. During the course of
this study we sometimes struggled to understand audit log messages that were
vague and possibly concerning. We believe that the following recommendations
will make audit files more usable.


\textbf{Vendors should document the meaning of all events.} Explanations of the different events that occur in the voting systems need to be more descriptive.  We found audit logs with the following event messages that were questionable, however we could not determine the gravity of the issue.
\begin{itemize}
	\item \textquotedblleft UNKNOWN\textquotedblright
	\item \textquotedblleft Warning - PEB I/O flag set\textquotedblright
	\item \textquotedblleft Warning - I/O flagged PEB will be used\textquotedblright
\end{itemize}

\textbf{Accuracy of date and time logging needs improvement.} Some voting
systems allow for system settings to be adjusted by election workers and
therefore are prone to human error. Time and date setting is one of the voting
machine parameters that is usually adjusted manually at election central in
preparation for precinct deployment. When the time of the machine setting is
incorrect, it becomes difficult to recreate election day events. Audit logs are
ground truth for election disputes; their accuracy is key. 

\textbf{Make system manuals available to the public.} Voting machine audit logs are public information. The general public can request them under the Freedom of Information (FOI) Act. In the same fashion, voting system manuals should be freely available so that the public can interpret the logs. 

\textbf{Some events are not currently logged, but they should be.} We believe
that important events can be added to the voting machine event logs. For
example, an event that records the time a ballot is activated would make it
easier to learn when the voting machines were heavily used and when they were idle.


