\smvertspace
\smsection{Future Voting System Suggestions}
Voting systems audit logs need to be comprehensible to the public. Ambiguous or
obscure messages make audit 
logs unusable to election officials and advocacy groups. During the course of
this study we sometimes struggled to understand audit log messages that were
vague, but concerning. We believe the following recommendations
will make audit files more usable.

\smvertspace
\begin{itemize}
\item Vendors should document the meaning of all events. %Explanations of the
%different events that occur in the voting systems should be descriptives, this
%is especially true for warning events.

%There isn't really a suggestion here, so I took it out. [CKS]
\begin{comment}
\textbf{Accuracy of date and time logging needs improvement.} Some voting
systems allow for system settings to be adjusted by election workers and
therefore are prone to human error. Time and date setting is one of the voting
machine parameters that is usually adjusted manually at election central in
preparation for precinct deployment. When the time of the machine setting is
incorrect, it becomes difficult to recreate election day events. Audit logs are
ground truth for election disputes; their accuracy is key. 
\end{comment}

\item Make system manuals available to the public. %Voting machine audit logs
%are public information. The general public can request them under the Freedom of
%Information (FOI) Act. In the same fashion, voting system manuals should be
%freely available so that the public can easily interpret the logs. 

\item Some events are not currently logged, but they should be. %We believe
%that important events can be added to the voting machine event logs. For
%example, an event that records the time a ballot is activated would make it
%easier to learn when the voting machines were heavily used and when they were idle.
\end{itemize}


