\subsection{Procedural Errors}
\smvertspace
It may be beneficial to election officials if they could detect at which
locations poll workers are following the required procedures. Procedural errors
can cause many problems including lost votes, incorrect vote counts, disgruntled
voters, and long lines. A few errors that might occur are: precincts that do not
print zero tapes on the morning of election day; using a master PEB to activate
ballots; and opening and closing machines with different PEBs. If election
officials are aware of the procedures that are not being followed, they could
improve their precinct checklist. This will allow for more efficient audits as
well as a better voting experience for voters. 

\smsubsubsection{Printing Zero Tapes}
This analysis pertains to jurisdictions that require poll workers to
print at least one zero tape per polling location. The printing of a zero tape
is important to verify that the voting machines are set to zero; it
ensures that additional votes will not be included in the certified
count. In this analysis we check if this procedure is followed.

In order to run this analysis, we require both a ballot image file, which
contains the machines and precincts, and an event log.  Given an event log that
has correct date and time stamps, and an event that represents the printing of a
zero tape, we can detect if this procedure was followed.  We limit our search of
the event log to events that occurred on election day.  We have noticed that the
zero tape may be printed before or after the official poll opening time, so we
do not specify time limitations.  Our analysis groups the machines found in the
event log by polling location using the ballot images file and requires at least
one machine per polling location have this event. If none of the
machines in a polling location record this event, we report the polling location
and the corresponding machines. 
%\cks{If multiple PEBs are used to open machines, but only one is used
%  for the zero tape, do you catch it?}

\smsubsubsection{Ballot Activation with a Master PEB}
Another procedure that should be avoided is using a master PEB to activate ballots for voters.  Poll workers should be using non-master (activator) PEBs to activate ballots for the reasons outlined in Section \ref{sec:background}.

This analysis focuses on procedures related to the use of the PEB and the voting
machine; it is applicable to other voting systems that use a similar process.
To detect violations of this procedure, the analysis requires that the event log
records votes being cast, machines being opened and closed, as well as the PEB
number used for each event.  Through this analysis we assign each machine a
master PEB: the PEB used to open and close the machine. Then, we check to see if
any votes were activated on each 
machine using the master PEB.  If we find any such cases, we report them.  In
the case that two different PEBs were
used to open and close the machine, our algorithm
checks both and if a ballot was activated with either one,
then that machine and PEB are reported.  


\smsubsubsection{Opening and Closing a Machine with Different PEBs}
\label{sec:opening_closing_diff_pebs}
Along the same lines, we report incidents of opening and closing a
machine with different PEBs. A machine should be opened and closed
with the master PEB; if not, it may be more likely that the non-master
PEB used for closing machines and its corresponding votes will be left behind at the precinct.  Poll workers are trained so that they put the master PEB, CF cards, and printed precinct tape in a designated bag, which is transported to election central after the precinct is closed.  

The requirements for this analysis are similar to the analysis discussed above.
As this analysis works with procedural errors concerning the interaction between
PEBs and the machine, it applies to systems that work in the same manner.  The
event log should contain events signaling the opening and closing of each
machine and the PEB used for each event.  In this analysis, we find the serial
numbers of the PEBs used to open and close each machine.  If the two PEBs have
conflicting numbers, then we report the machine and PEB serial numbers.  If the
PEBs are the same, then the correct procedure was followed and no machines are
reported.  


\smsubsubsection{Anomalous Vote Cancelled Events}
There may be
many reasons why votes are cancelled. According to the iVotronic’s event logs
there are seven options for canceling a ballot. Depending on the reason chosen, it
might be possible to identify procedural errors.  For example, if there are any
instances of canceling a ballot due to a printer problem, it could be an
indicator of a procedural error because ballots are not normally printed. In other
cases, if there is a large number of a specific reason, such as having the wrong
ballot, this could indicate the poll workers are repeatedly issuing the wrong
ballot or the terminal is experiencing calibration issues.  

This analysis has a higher potential to be used on other voting systems than the
previous two analyses.  It only requires that the event log record
votes being cancelled, and reasons as to why the vote is being cancelled.  This
analysis would perform best if the date and time stamp were accurate as well.
For each machine, we associate with it the number of each type of vote
cancellation recorded and report the
machines that had at least one vote cancellation event type that occurred an
unusually high number of times. In our analysis, an \textquotedblleft unusually
high number of times\textquotedblright \hspace{1 mm} is defined as having a
number of instances greater than three standard deviations above the average for
that event type.
If it is the case, we will also report if a machine has an unusually high
number of instances for more than one vote cancellation event type, and which
event types they are.  


