\subsection{Procedural Errors}
It may be beneficial to election officials if they could detect at which locations poll workers are following the required procedures. Procedural errors can cause many problems including lost votes, incorrect vote counts, disgruntled voters, and long lines. A few of these are: precincts that do not print zero tapes on the morning of election day; using a master PEB to activate ballots; opening and closing machines with different PEBs. If election officials are aware of the procedures that are not being followed, they could review their precinct checklist. This will allow for more efficient audits as well as a better voting experience for voters.

\subsubsection{Printing Zero Tapes}
This analysis pertains to jurisdictions that require poll workers to print at least one zero tape per polling location.  According to the South Carolina poll worker training video (citation), poll workers are required to print at least one zero tape per polling location on the morning of the election.  We check if this procedure is followed.  The printing of a zero tape is important to verify that the public count is set to zero; it ensures that additional votes will not be included in the certified count.  

In order to run this analysis, we require both a ballot images file (that contains the machines and polling locations) and an event log.  Given that the event log that has correct date and time stamps, and an event that represents the printing of a zero tape, we can detect if this procedure was followed.  We limit our search of the event log to events that occurred on election day.  We have noticed that the zero tape may be printed before or after the official poll opening time, so we do not specify time limitations.  Our analysis groups the machines found in the event log by polling location using the ballot images file.  Then we crosscheck the list of machines with the specified event; our analysis only requires at least one machine per polling location to have this event.  If none of the machines in a polling location record this event, we report the polling location and the corresponding machines.

\subsubsection{Ballot Activation with a Master PEB}
Another procedure that should be avoided is using a master PEB to activate ballots for voters.  Poll workers should be using non-master PEBs to activate ballots so that the PEBs do not get switched or misplaced.  If this happens, it is easier for the poll workers and election officials to forget that they should upload votes from a non-master PEB; this could result in lost votes.

This analysis focuses on procedures related to the use of the PEB and the machine; it is applicable to other voting systems that use a similar process.  To detect violations of this procedure, the analysis requires that the event log records votes being cast, machines being opened and closed, and the PEB number used for each event.  Through this analysis we assign each machine a master PEB, which is the PEB used to open and close the machine; by doing this, we are assuming that the machine was opened and closed with the master PEB.  Then, we check to see if any votes were cast on each machine using the master PEB.  If we find any such cases, we report them.  

\subsubsection{Opening and Closing a Machine with Different PEBs}
Along the same lines, we report incidents of opening and closing a machine with different PEBs. A machine should be opened and closed with the same master PEB; if not, it may be more likely that this PEB does not get uploaded and votes do not get counted.

The requirements for this analysis are similar to the analysis discussed above.  As this analysis works with procedural errors concerning the interaction between PEBs and the machine, it applies to systems that work in the same manner.  The event log should contain events signaling the opening and closing of each machine and the PEB used for each event.  In this analysis, we find the PEB used to open a machine and the PEB used to close a machine.  If the two PEBs have conflicting numbers, then we report the machine serial number and the PEB numbers.  If the PEBs are the same, then the procedure was followed.  

\subsubsection{Anomalous Vote Cancelled Events}
When poll workers cancel ballots, they must select a reason why; this is another way to detect errors. There could be many reasons why votes are cancelled; according to the iVotronic’s event logs there are seven options for canceling a ballot: \textquotedblleft wrong ballot,\textquotedblright \hspace{1 mm} \textquotedblleft voter left after the ballot,\textquotedblright \hspace{1 mm}  \textquotedblleft voter left before the ballot,\textquotedblright \hspace{1 mm}  \textquotedblleft voter request,\textquotedblright \hspace{1 mm}  \textquotedblleft printer problem,\textquotedblright \hspace{1 mm}  \textquotedblleft terminal problem,\textquotedblright \hspace{1 mm}  or \textquotedblleft other reason.\textquotedblright \hspace{2 mm}  Depending on the various reasons, other conclusions could be made.  For example, if there are any instances of canceling a ballot due to a printer problem, it could be an indicator of a procedural error because ballots are not printed. In other cases, if there is a large number of a specific reason, such as having the wrong ballot, this could indicate the poll workers are repeatedly issuing the wrong ballot.  

This analysis has a higher potential to be used on other voting systems than the previous two analyses.  This analysis only requires the event log record votes being cancelled, and reasons as to why the vote is being cancelled.  This analysis would perform best if the date and time stamp were accurate as well.  For each machine, we associate it with how many instances of each type of vote cancellation are recorded on it.  We expect some “normal” number of instances of each vote cancellation event, but we do not know what this “normal” number is.  To find this we need the average number of each vote cancellation type; therefore, the analysis has seven averages to calculate.  Next we calculate the standard deviation for each of these event types.  After analyzing each machine’s event history, we report the machines that had at least one vote cancellation event type that occurred an unusually high number of times; in our analysis, an “unusually high number of times” is defined as having a number of instances greater than three standard deviations above the average.  If it is the case, we will also report if a machine records this unusually high number of instances for more than one vote cancellation event type, and which event types they are.  


