\section{Related Work}
Many election technology systems provide a possible means of auditing elections. For example, in optical scanning systems the cast ballots themselves form a paper record of the votes cast on election day. On the other hand, DRE machines do not provide this type of paper trail. Some DREs provide a Voter Verified Paper Audit Trail (VVPAT), which stores a hard copy version of each ballot cast. The paper ballot can be read, but not modified, by the voter at the time of casting their vote. A third type of audit trail, which is produced by all DREs, are the event logs stored electronically on each DRE. Our work pertains to the elections in South Carolina, which do not require the creation of a paper trail, but do provide the audit logs from the machines. In this section we discuss related work on the analysis of audit logs for post-election auditing.

Two recent studies, which analyzed the iVotronic audit logs, focused on the verification of election results~\cite{Buell2011,Sandler2007}. The authors of the first study~\cite{Buell2011} performed an audit of the same South Carolina elections that we analyzed. Using these audit logs, they discovered uncounted votes and problems with the audit data. By consulting additional audit materials, such as the printed results tapes, the authors were able to offer possible reasons and explanations as to why the problems occurred. Our work takes a slightly different approach. We focus on providing a fully automated web-based tool that election officials might use and therefore we do not refer to printed results tapes or other material aside from the audit logs in our analysis. While our tool did discover and report these same problems, we simply report what was wrong, but can not provide a possible explanation for the cause of the error. 

The authors of the second study~\cite{Sandler2007} provided an analysis of vote tallies using the protected count of votes on each machine and comparing this to the printed results tapes. Their report also finds dates that were most likely inaccurate.  With further investigation, they concluded that the hardware clock was incorrect. Our research provides analyses to identify similar problems, but in a way that could be automated.

There has also been research on using the audit logs to analyze election-day procedure and activity. For example, one recent publication showed how event logs could be used to determine if a machine acted \textquotedblleft normally\textquotedblright on election day~\cite{Antonyan2009}. The authors of this research studied the event logs of the AccuVote Optical Scanning system and used those logs to build a finite state machine that models the sequences of events a well-behaved machine might produce. This type of analysis would be useful to provide for the iVotronic systems that we studied. However, the AccuVote machines have considerably fewer possible event types than the iVotronics so the analysis would become considerably more complex.

A common problem on election day, which we try to identify in our analysis, is the occurrence of long lines. Many studies have researched ways to mitigate long lines at polling locations ~\cite{Allen2006,Dow2007,Spencer2010,Wilson2008}.  One such study has simulated the flow of voters through the voting process at polling location~\cite{Edel2010}. The authors use this simulation to determine the optimal number of voters per voting machine, and correspondingly, the correct number of voting machines per polling location based on the number of registered voters at that particular location. Their work is predictive: the authors make some assumptions, such as the average time it takes to vote and when peak voting hours will occur, and use those as a basis for predicting where long lines are likely to occur. Our analysis is descriptive: given the audit logs from election day, we infer the average time it took to vote and use that information to determine whether a particular polling location experienced long lines or not. The two methods are complementary. Predictive models can be used to prevent long lines, while descriptive models can be used to check and refine the prediction algorithms.

Voter Verified Paper Audit Trails (VVPATs) are a different type of audit log. Unlike the audit logs we used in our analyses, VVPATs are viewed and verified by the voter and are more suited to audits concerning a DRE incorrectly capturing a voter\textquoteright s intent. Our work is more concerned with identifying cases of cast votes not being included in the final count, or issues at the polling place that might prevent the voter from casting their vote in the first place. With VVPATs, as long as a certain percentage of voters do check their paper ballot~\cite{Hall2006}, the voting machine need not be assumed correct, whereas our analyses do make this assumption.
